Spike spectra for recurrences

### 2022-11-02 Manuscript/inter_spike_manuscript_mdpi.tex
Roessler example: Added figures for noise analysis

The inter-spike spectra unravel the specific dynamics, which are also apparent in the state space portraits (Fig.~\ref{fig_tau_rr_example_roessler}A, B, C) and in the 
$\tau$-RRs (Fig.~\ref{fig_tau_rr_example_roessler}G, H, I). The proposed idea is also 
robust to noise (see Fig.~\ref{fig_tau_rr_example_roessler_noise} in the Appendix). This is because the peaks of the $\tau$-RR are insensitive to noise. While the peak shape does 
change in the presence of noise, its position does not, and this is what the inter-spike spectrum encrypts after all.

@@

\acknowledgments{
All computations have been carried out in MATLAB\textsuperscript{\textregistered} and the Julia language 
and made use of the packages \textit{DynamicalSystems.jl} \cite{datseris2018} and \textit{DifferentialEquations.jl} \cite{rackauckas2017}.
}

@@

>>>>

The inter-spike spectra unravel the specific dynamics, which are also apparent in the state space portraits (Fig.~\ref{fig_tau_rr_example_roessler}A, B, C) and in the 
$\tau$-RRs (Fig.~\ref{fig_tau_rr_example_roessler}G, H, I). The proposed idea is also 
robust to noise (see Fig.~\ref{fig_tau_rr_example_roessler_noise} in the Appendix). This is because the peaks of the $\tau$-RR are insensitive to noise. 
Figure \ref{fig_roessler_peaks} illustrates that 
while the peak shape does change in the presence of noise, its position does not, and this is what the inter-spike spectrum encrypts after all 
(see Fig.~\ref{fig_roessler_spectra_distances} in the Appendix for further analysis).

\begin{figure}
 \centering
 \includegraphics[width=0.9\textwidth]{./figures/fig_roessler_different_noise_levels_peaks}
 \caption{Peak positions of the obtained inter-spike spectra of the $\tau$-RRs for additive noise levels up to 50\% for the discussed R\"ossler dynamics, 
 \textbf{A} period-2 limit-cycle, \textbf{B} period-3 limit-cycle and \textbf{C} chaos. The size of the plotted markers scale with the detected peak height. The noise-free spectra are shown in Fig.~\ref{fig_tau_rr_example_roessler}J, K, L and 
 an example of these spectra with 5\% additive noise is shown in Fig.~\ref{fig_tau_rr_example_roessler_noise}J, K, L. Spectra were obtained with a LASSO regression and a regularization threshold 
  corresponding to $\rho=0.95$ accordance of $\tau$-RRs and re-composed signals.}
\label{fig_roessler_peaks}
\end{figure}

@@

\acknowledgments{
All computations have been carried out in MATLAB\textsuperscript{\textregistered} and the Julia language 
and made use of the packages \textit{DynamicalSystems.jl} \cite{datseris2018}, \textit{DifferentialEquations.jl} \cite{rackauckas2017}, \textit{Distances.jl} and 
\textit{OptimalTransport.jl} \cite{Zhang2022}.
}

@@

\begin{figure}[h!]
 \centering
 \includegraphics[width=0.9\textwidth]{./figures/fig_roessler_spectra_distances}
 \caption{Wasserstein distances for the obtained inter-spike spectra of the $\tau$-RRs for additive noise levels up to 50\% for the discussed R\"ossler dynamics, 
 \textbf{A} period-2 limit-cycle, \textbf{B} period-3 limit-cycle and \textbf{C} chaos. For each noise level the obtained spectrum is compared to the noise-free spectrum (these are shown 
 in Fig.~\ref{fig_tau_rr_example_roessler}J, K, L for a regularization threshold corresponding to $\rho=0.95$) by computing its Wasserstein distance. Inter-spike spectra were obtained with a 
 LASSO regression and three different regularization thresholds corresponding to $\rho=0.9$ (blue), $\rho=0.95$ (orange) and $\rho=0.99$ (green) accordance of $\tau$-RRs and re-composed signals. 
 Up to a noise level of 20\% the distances are small and rather constant. The fluctuations depend on the chosen regularization threshold as well as on the underlying dynamics.}
\label{fig_roessler_spectra_distances}
\end{figure}
